A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-24 paper.tex

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\Hod}{\mathrm{Hod}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\ML}{\mathrm{ML}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\renewcommand{\U}{\mathrm{U}}

@@

\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, integration $\int_{X\times Y\times M} \Omega_X\wedge (-)$ and the pairing $\langle -, -\rangle$ on $\fg$.

@@

\begin{example}
Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$. Consider the dg Lie algebra
\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$. The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself. The space of fields in the corresponding Chern--Simons theory will be denoted by
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]

Note that if $X$ is merely a complex manifold equipped with a square root $K_X^{1/2}$ of the canonical bundle, we may still define the Chern--Simons theory with the bundle of BV fields
\begin{align*}
E = &\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \\
\oplus &\Omega^{0,\bu}_X\otimes K_X^{1/2} \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes V \\
\oplus &\Omega^{\dim_\CC X,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg^*[d-2]
\end{align*}
and the action functional as before.
\label{ex:CSHamiltonianreduction}
\end{example}

@@

\begin{prop}
Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure. Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, V\ham\fg).\]
Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
\end{prop}

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.

This theory admits three twists:
\begin{itemize}
\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm} = 0$. These are holomorphic. Moreover, we have an isomorphism $\alpha\colon \U(1)\xrightarrow{\sim} \Spin(2, \RR)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory. Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$. We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\cong G_R$, so the twisted theory carries an action of $\MU(4)$.

@@

\item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$. The supercharge $Q_+$ is stabilized by $\SU(4)\subset \Spin(8, \RR)$. The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$. We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
\end{itemize}

@@

We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \RR)$ under which $Q$ becomes scalar. Moreover, we have an isomorphism $\alpha\colon \U(1)\cong\Spin(2, \RR)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action. In fact, this action will factor through $\U(4)$ by a direct observation.

@@

\begin{theorem}
The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $\map(M, T^*[3] B\fg)$. Moreover, the equivalence is $\U(4)$-equivariant.
\label{thm:8dholomorphictwist}
\end{theorem}
\begin{proof}
8d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 10d $\cN=1$ super Yang--Mills theory. Under dimensional reduction the 10d fields from Section \ref{sect:10dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt\phi \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
\rho&\rightsquigarrow \rho, \wt\chi \\
B&\rightsquigarrow B, C.
\end{align*}

The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}). We are left to check that the equivalence respects  the gradings and the $\U(4)$-action. Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
&&\ar@{}^{\bigoplus}[r] &&& \\
\Omega^{4,0}(\CC^4; \gg)_{\phi} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
}
\]
concentrated in cohomological degrees $-2, \dots, 3$. These fields have the same degrees as in the holomorphic BF theory.
\end{proof}

@@

Finally we discuss the case of the partially topological supercharge $(Q_+, Q_-)\in\Sigma$. We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \RR)$ given by projection on the second factor.

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.

This theory admits three twists:
\begin{itemize}
\item Rank 1 supercharges $Q=\alpha\otimes w\in S\otimes W$, where $(\alpha, \alpha)_S = 0$. These are minimal, i.e. the number of invariant directions is 4. We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$. We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \RR)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.

\item Rank 1 supercharges $Q = \alpha \otimes w \in S \otimes W$, where $(\alpha, \alpha)_S\neq 0$. These are topological and stabilized by $G_2\subset \Spin(7, \CC)$. We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \RR)$ under which they have weight $1$.

\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor, so tht theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
\end{itemize}

@@

The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$. We consider the grading $\alpha\colon \U(1)\rightarrow G_\RR$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\U(1)\times \Spin(N_\RR).\]

\begin{theorem}
The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, T^*[3] B\fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:8dBFreduction}
\end{theorem}
\begin{proof}
By Theorem \ref{thm:8dholomorphictwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory. Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant. By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $\map(L\times N_\RR, T^*[3] B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

@@

\begin{theorem}
The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:7dminimaltwist}
\end{theorem}

@@

Finally, we discuss the case of a partially topological twist. We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor.

@@

The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall. Let $U$ be a complex symplectic $\fg$-representation. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure. The $R$-symmetry group depends on the type of the representation $U$:
\begin{itemize}
\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.

\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
\end{itemize}

This theory admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions, so it gives rise to a holomorphic theory. If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \U(1)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading. Such a supercharge is stabilized by $G=\SU(3)\subset \Spin(6, \CC)$. We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(3)$-action.
\end{itemize}

@@

We fix an embedding $\U(1)\subset \SU(2)$ under which $w_1\in W_+$ has weight $1$. Under the composite
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
we obtain that $W_+\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.

@@

\begin{theorem}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{theorem}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a new twisting homomorphism
\[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

@@

The identity map $\alpha\colon \U(1)\cong G_R$ makes $Q$ weight $1$.

>>>>

\newcommand{\BV}{\mathrm{BV}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\newcommand{\gauge}{\mathrm{gauge}}
\newcommand{\Gm}{\mathbb{G}_m}
\newcommand{\Hod}{\mathrm{Hod}}
\newcommand{\matter}{\mathrm{matter}}
\newcommand{\ML}{\mathrm{ML}}
\newcommand{\MU}{\mathrm{MU}}
\renewcommand{\Re}{\mathrm{Re}}
\newcommand{\Sect}{\mathrm{Sect}}
\renewcommand{\U}{\mathrm{U}}

@@

\item The pairing $\omega\colon E\otimes E\rightarrow \Dens_M[-1]$ is given by the combination of the wedge product of differential forms, wedging with $Omega_X$ and the pairing $\langle -, -\rangle$ on $\fg$.

@@

\begin{example}
Let $X,Y,M$ be as before and denote $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M)$. Suppose $\fg$ is a dg Lie algebra and $V$ is a $\fg$-representation equipped with a $(d-1)$-shifted symplectic structure $V\otimes V\rightarrow  \CC[d- 1]$. Consider the dg Lie algebra
\[\cL = \fg\oplus V[-1]\oplus \fg^*[d-3]\]
with the brackets $\fg\otimes \fg\rightarrow \fg$ given by the Lie bracket on $\fg$, $\fg\otimes V\rightarrow V$ given by the $\fg$-action on $V$, $\fg\otimes \fg^*\rightarrow \fg^*$ given by the coadjoint action and $\mu\colon V\otimes V\rightarrow \fg^*[d-1]$ defined by $(\mu(v, w), x)_\fg = ([x, v], w)_V$. The dg Lie algebra $\cL$ carries nondegenerate invariant symmetric pairing of cohomological degree $d-3$ given by pairing $\fg$ and $\fg^*$ and pairing $V$ with itself. The space of fields in the corresponding Chern--Simons theory will be denoted by
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, V \ham \fg):= \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \cL).\]
\label{ex:CSHamiltonianreduction}
\end{example}

We will also sometimes use the following variant of the generalized Chern--Simons theory (see also \cite{GinzburgRozenblyum}).

\begin{definition}
Let $m$ be a positive integer. Suppose $X$ is a complex manifold equipped with an $m$-th root $K_X^{1/m}$ of the canonical bundle, $Y, M, \fg$ are as before and $\fg$ is equipped with a weight grading $\fg=\oplus_n \fg(n)$ for which the symmetric pairing $\langle -, -\rangle$ on $\fg$ has weight $m$. We may consider a version of the generalized Chern--Simons theory with the bundle of BV fields
\[E = \bigoplus_n \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg(m)\otimes K_X^{n/m} [1]\]
and the symplectic pairing $\omega$ and the action functional as before where we do not use the holomorphic volume form on $X$.
\end{definition}

We denote the space of fields $\cE = \Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg\times_{\Gm} K_X^{1/m})$.

\begin{example}
Consider the setting of Example \ref{ex:CSHamiltonianreduction}. The dg Lie algebra $\cL$ carries a weight grading, where we consider $\fg$ in weight 0, $V$ in weight $1$ and $\fg^*$ in weight $2$. With respec to this weight grading the bilinear pairing on $\fg$ has weight $2$, so we may define the corresponding generalized Chern--Simons theory with the space of fields
\[\Sect(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, (U\otimes K_X^{1/2})\ham \fg).\]
\end{example}

@@

\begin{prop}
Suppose $\fg$ is a dg Lie algebra and $V$ a $\fg$-representation equipped with a $(n_1+2n_2+n_3-1)$-shifted symplectic structure. Consider the generalized Chern--Simons theory on $\RR^{2n_1+2n_2+n_3}$ with the space of BV fields
\[\cE = \map(\CC^{n_1}\times (\CC^{n_2})_{\mr{Dol}}\times (\RR^{n_3})_{\mr{dR}}, (V\otimes K_{\CC^{n_1}}^{1/2})\ham\fg).\]
Then it carries an action of $\MU(n_1)\times \U(n_2)\times \SO(n_3)$ given by the pullback action on differential forms on $\CC^{n_1}\times \CC^{n_2}\times \RR^{n_3}$.
\end{prop}

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \CC)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.

This theory admits three twists:
\begin{itemize}
\item Supercharges $(Q, 0)$ and $(0, Q)$ with $(Q, Q)_{S_\pm} = 0$. These are holomorphic. Moreover, we have an embedding $\alpha\colon \U(1)\hookrightarrow \Spin(2, \CC)$ under which they have weight 1, so they give rise to a $\ZZ$-graded holomorphic theory. Such a supercharge is stabilized by $G=\SU(4)\subset \Spin(8, \CC)$. We have a twisting homomorphism $\phi\colon \MU(4)\xrightarrow{\det^{1/2}} \U(1)\xrightarrow{\alpha} G_R$, so the twisted theory carries an action of $\MU(4)$.

@@

\item Square-zero supercharges $(Q_+, Q_-)$ where both $Q_{\pm}$ are nonzero. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have $(Q_\pm, Q_\pm)_{S_\pm} = 0$. The supercharge $Q_+$ is stabilized by $\SU(4)\subset \Spin(8, \RR)$. The supercharge $Q_-$ is stabilized by $\SU(3)\subset \SU(4)\subset \Spin(8, \RR)$. We have a twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \CC)$ given by projection onto the second factor, so the twisted theory in fact carries an action of $\SU(3)\times \Spin(2, \RR)$.
\end{itemize}

@@

We consider the twisting homomorphism $\det^{1/2}\colon \MU(4)\rightarrow \Spin(2, \CC)$ under which $Q$ becomes scalar. Moreover, we have an embedding $\alpha\colon \U(1)\subset\Spin(2, \CC)$, so the theory is $\ZZ$-graded and carries an $\MU(4)$-action. In fact, this action will factor through $\U(4)$ by a direct observation.

@@

\begin{theorem}
The holomorphic twist of 8d $\cN=1$ super Yang--Mills on $M=\RR^8$ is perturbatively equivalent to the holomorphic BF theory on $M\cong\CC^4$ with the space of fields $T^*[-1]\map(M, B\fg)$. Moreover, the equivalence is $\U(4)$-equivariant.
\label{thm:8dholomorphictwist}
\end{theorem}
\begin{proof}
8d $\cN=1$ super Yang--Mills theory is obtained by dimensionally reducing 10d $\cN=1$ super Yang--Mills theory. Under dimensional reduction the 10d fields from Section \ref{sect:10dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \wt\phi \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, \phi \\
\rho&\rightsquigarrow \rho, \wt\chi \\
B&\rightsquigarrow B, C.
\end{align*}

The claim about the underlying $\ZZ/2$-graded theories follows by applying dimensional reduction (Proposition \ref{CS_to_BF_diml_red_prop}) to the computation of the minimal twist of 9d $\cN=1$ super Yang--Mills (Theorem \ref{thm:9dminimaltwist}). We are left to check that the equivalence respects  the gradings and the $\U(4)$-action. Indeed, the equivalence given by Theorem \ref{thm:9dminimaltwist} eliminates fields $A_{1, 0}, \wt\phi, \rho, \chi, \wt\chi$ and hence the underlying local $L_\infty$ algebra after the twist becomes
\[
\xymatrix@R=0.5cm@C=0.5cm{
&\Omega^0(\CC^4; \gg)_c \ar[r] &\Omega^{0,1}(\CC^4; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^4; \gg)_{B} \ar[r] &\Omega^{0,3}(\CC^4; \gg)_{C^*} \ar[r] &\Omega^{0,4}(\CC^4; \gg)_{\phi^*} \\
&&\ar@{}^{\bigoplus}[r] &&& \\
\Omega^{4,0}(\CC^4; \gg)_{\phi} \ar[r] &\Omega^{4,1}(\CC^4; \gg)_C \ar[r] &\Omega^{4,2}(\CC^4; \gg)_{B^*} \ar[r] &\Omega^{4,3}(\CC^4; \gg)_{A_{0,1}^*} \ar[r] &\Omega^{4,4}(\CC^4; \gg)_{c^*}&
}
\]
concentrated in cohomological degrees $-1, \dots, 4$. These fields have the same degrees as in the holomorphic BF theory.
\end{proof}

@@

Finally we discuss the case of the partially topological supercharge $(Q_+, Q_-)\in\Sigma$. We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(2, \RR)\rightarrow G_R=\Spin(2, \CC)$ given by projection on the second factor.

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \CC)$ with $W$ the two-dimensional spin representation.

This theory admits three twists:
\begin{itemize}
\item Rank 1 supercharges $Q=\alpha\otimes w\in S\otimes W$, where $(\alpha, \alpha)_S = 0$. These are minimal, i.e. the number of invariant directions is 4. We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R=\Spin(3, \CC)$ under which they have weight $1$. We also have a twisting homomorphism $\phi\colon \MU(3)\xrightarrow{\det^{1/2}} \U(1)\rightarrow \Spin(3, \CC)$, so the twisted theory is $\ZZ$-graded and carries an action of $\MU(3)$.

\item Rank 1 supercharges $Q = \alpha \otimes w \in S \otimes W$, where $(\alpha, \alpha)_S\neq 0$. These are topological and stabilized by $G_2\subset \Spin(7, \CC)$. We have a homomorphism $\alpha\colon \U(1)\rightarrow G_R$ under which they have weight $1$.

\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \CC)$ given by projection on the second factor, so the theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
\end{itemize}

@@

The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\Spin(2, \CC)\times \Spin(N_\RR)$. We consider the grading $\alpha\colon \U(1)\rightarrow G_R$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\Spin(2, \RR)\times \Spin(N_\RR).\]

\begin{theorem}
The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1] \map(L\times (N_\RR)_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:8dBFreduction}
\end{theorem}
\begin{proof}
By Theorem \ref{thm:8dholomorphictwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory. Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant. By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

@@

\begin{theorem}
The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\map(\CC^3\times \RR_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:7dminimaltwist}
\end{theorem}

@@

Finally, we discuss the case of a partially topological twist. We consider the twisting homomorphism $\phi\colon \SU(3)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \CC)$ given by projection on the second factor.

@@

The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sect:SYM} which we now recall. Let $U$ be a complex symplectic $\fg$-representation. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure. The $R$-symmetry group depends on the type of the representation $U$:
\begin{itemize}
\item In general, the theory admits an $R$-symmetry group $G_R=\SL(2, \CC)$ with $W_+$ the two-dimensional defining representation.

\item If $U = T^* R=R\oplus R^*$ for a $\fg$-representation $R$, then the theory admits an $R$-symmetry group $G_R=\SL(2, \CC)\times \GL(1, \CC)$, where $\GL(1, \CC)$ acts trivially on $W_+$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
\end{itemize}

This theory admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions, so it gives rise to a holomorphic theory. If the representation $U$ is of cotangent type, we have a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R=\SL(2, \CC)\times \GL(1, \CC)$ given by a diagonal embedding, so in this case we get a $\ZZ$-grading. Such a supercharge is stabilized by $G=\SU(3)\subset \Spin(6, \CC)$. We have a twisting homomorphism $\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SL(2, \CC)$, so the twisted theory carries an $\MU(3)$-action.
\end{itemize}

@@

We fix an embedding $\U(1)\subset \SL(2, \CC)$ under which $w_1\in W_+$ has weight $1$. Under the composite
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\subset \SL(2, \CC)\]
we obtain that $W_+\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.

@@

\begin{theorem}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\Sect(M, (U\otimes K_M^{1/2})\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{theorem}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SL(2, \CC)\times \GL(1, \CC)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SL(2, \CC)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a new twisting homomorphism
\[\Tilde{\phi}\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

@@

The embedding $\alpha\colon \U(1)\hookrightarrow G_R$ makes $Q$ weight $1$.
